Meta-analytic approaches and effect sizes to account for 'nuisance heterogeneity' in comparative physiology

### 2021-09-17 MS/ms.Rmd
Fixed BPA to generalise a bit to pollutants

# Maybe add some examples for each effect size in a new column. SHould help
eg <- c("CTmin, CTmax, LC50, LT50, Metabolic Rate (MR)",
        "Variability in CTmin, CTmax, Metabolic Rate (MR)",
        "Ratio between BPA treatment (BPA-exposed group) and control (no BPA)",
        "Difference in immune response between males and females or performance difference in the presence of stressor compared to absence of stressor",
        "Relationship between sex hormones and immune responses or metabolic rate and behaviour")

>>>>

# Maybe add some examples for each effect size in a new column. SHould help
eg <- c("CTmin, CTmax, LC50, LT50, Metabolic Rate (MR)",
        "Variability in CTmin, CTmax, Metabolic Rate (MR)",
        "Ratio between pollutant exposed treatment (e.g., BPA-exposed group) and control (no pollutant)",
        "Difference in immune response between males and females or performance difference in the presence of stressor compared to absence of stressor",
        "Relationship between sex hormones and immune responses or metabolic rate and behaviour")
